---
title: "Using k-Means to Cluster Tweets"
author: "Jana Osea and Evan Quan"
date: "November 24, 2020"
output: html_document
---

```{r setup, include=FALSE}
all_pkgs <- c("factoextra","tidyverse","twitteR", "tidytext", "hash", "openssl", "httpuv", "gridExtra", "hrbrthemes", "kableExtra")
sapply(all_pkgs, library, character.only=TRUE, logical.return=TRUE)
```

## Dataset Previews

We will use three datasets scraped from Twitter on November 22, 2020 using $n=100$ tweets.

1. Raw Scraped Dataset

```{r, echo=FALSE}
source("tweet-scraping.R")
source("data-transform.R")

# ======================= INPUT =========================
word <- "biden"
n <- 100
data <- scrape_tweets(word, n, live=FALSE)
tweets <- as.data.frame(data[1])
df <- as.data.frame(data[2])
common_words <- as.data.frame(data[3])
```


    ```{r, echo=FALSE}
    head(tweets, 3) %>%
      kbl() %>%
      kable_styling()
    ```

2. Processed Scaled Tweets

    ```{r, echo=FALSE}
    head(df, 3) %>%
      kbl() %>%
      kable_styling()
    ```

3. Top 10 Common Words

    ```{r, echo=FALSE}
    head(common_words, 3) %>%
      kbl() %>%
      kable_styling()
    ```
    
## k-Means Clustering 

We plotted the cluster plots with $k=2,3,4,5$ clusters correspondingly.
```{r, echo=FALSE}
k2 <- kmeans(df,2,nstart=25)
k3 <- kmeans(df,3,nstart=25)
k4 <- kmeans(df,4,nstart=25)
k5 <- kmeans(df,5,nstart=25)

# plots to compare
p1 <- fviz_cluster(k2, geom = "point", data = df) + ggtitle("k = 2")
p2 <- fviz_cluster(k3, geom = "point",  data = df) + ggtitle("k = 3")
p3 <- fviz_cluster(k4, geom = "point",  data = df) + ggtitle("k = 4")
p4 <- fviz_cluster(k5, geom = "point",  data = df) + ggtitle("k = 5")
grid.arrange(p1, p2, p3, p4, nrow = 2)
```

We choose $k=3$ as our chosen number of clusters and we will now analyze.

## $k=3$ Means Clustering Analysis

#### Variation Between, Within and Total

```{r, echo=FALSE}
data.frame("Sum of Squares"= c("Between", "Total"), Values=c(k3$betweenss, k3$totss)) %>% kbl() %>%
kable_styling()
data.frame(Cluster= c(1,2,3),'Within Sum of Squares' =c(k3$withinss)) %>% kbl() %>%
kable_styling()
```

#### 1. Common Words

```{r, echo=FALSE}
tweets$cluster <- k3$cluster
# plot of 10 most common words
p5 <- ggplot(common_words, aes(x = reorder(word, n, function(n) -n), y=n)) + 
  geom_bar(stat="identity", fill="lightblue")+ theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  xlab("") + ggtitle("Top 10 Most Common Words")
p5
```
    
#### 2. Hot Word Scores

```{r, echo=FALSE}
p6 <- count(tweets, cluster, score) %>% ggplot( aes(fill=score, y=n, x=cluster)) + 
  geom_bar(position="stack", stat="identity")+theme_minimal() + 
  ggtitle("Score Distribution Grouped by Clusters")
p6
```

#### 3. Compare Characteristics of Each Cluster

```{r, echo=FALSE}
p7 <- quantile_plot(tweets$retweetCount, tweets$cluster) + ggtitle("Retweet Count")
# compare follower count in each cluster
p7
p8 <- quantile_plot(tweets$followers, tweets$cluster) + ggtitle("Followers Count")
p8
# compare total tweets count in each cluster
p9 <- quantile_plot(tweets$total_tweets, tweets$cluster) + ggtitle("Total Tweets Count")
p9
grid.arrange(p7, p8, p9, nrow = 2)
```


#### 4. Top 5 Nearest Tweets to Each Centroid Cluster

```{r, echo=FALSE}
top_5 <- top_n_tweets(tweets,k3,5)
top_5 %>% group_by(cluster) %>% select(screenName, followers, total_tweets, location, score) %>% kbl() %>%
kable_styling()
```


